Using Distributed Information Stores for Patient-Clinician Health Data Sharing

### 2013-01-16 patient-clinician-workshop/pccworkshop.tex
boo

In this position paper, we look at the potential and problems of
augmenting the next generation of EHRs with personal \emph{activity
  diaries}, portraits of a person's dynamic condition captured at high
temporal fidelity.  Such activity diaries are intended to supplement,
rather than supplant, the existing diagnostic reports performed by
professionals, first and foremost, to help clinicians derive a more
complete picture of the person throughout a period of care, such as an
intervention.  We believe that such activity diaries could potentially
also be beneficial to individuals as well, making people more aware of
the evolution of their health.

>>>>

In this position paper, we look at the potential and problems of
augmenting the next generation of EHRs with personal \emph{activity
  diaries}, portraits of a person's dynamic condition captured at high
temporal fidelity.  Such activity diaries are intended, first and
foremost, to supplement, rather than supplant the existing diagnostic
reports performed by professionals, in order provide clinicians with a
more complete picture of a patient's life throughout a period of care.
We believe that such activity diaries could potentially also be
beneficial to individuals as well, making people more aware of the
evolution of their health.
